\cvsection{Experience}
\begin{cventries}
\cventry
    {Student Developer}
    {Alex Solutions, Intelligent Tagging Team}
    {Victoria, Australia}
    {Jan. 2020 – PRESENT}
    {
      \begin{cvitems}
        \item {Peformed software development and quality assurance roles for Alex, a metadata managment system.}
        \item {My team uses machine learning to classify metadata into appropriate business concepts, subsequently used as overlay to enhance information presented to users about their data assets. Worked with Java, Python, React, Neo4j, and automated testing tools.}
      \end{cvitems}
    }
	\cventry
    {Teaching Associate}
    {Monash University}
    {Victoria, Australia}
    {Jul. 2019 – Dec. 2020}
    {
      \begin{cvitems}
        \item {Tutor for FIT1045 Introduction to programming fundamentals in Python. The subject introduces basic algorithms, data structures, problem-solving paradigms, and algorithm analysis.}
      \end{cvitems}
    }
    \cventry
    {Chief Investigator, CURIE Undergraduate Research Fellow}
    {Monash University}
    {Victoria, Australia}
    {Aug. 2019 – PRESENT}
    {
      \begin{cvitems}
        \item {Conducting research exploring the viability of student-led pro bono IT services for small non-profit organisations.}
        \item {Competitively selected and awarded \$2800 by the Centre for Undergraduate Research Initiatives and Excellence (CURIE) to carry out the project.}
      \end{cvitems}
    }
  \cventry
    {Platoon Commander, Signal Officer}
    {Singapore Armed Forces}
    {Singapore}
    {Jul. 2016 – May. 2017}
    {
      \begin{cvitems}
        \item {Oversaw the day-to-day operations of a platoon in a high-readiness battalion, planning and conducting operations and training exercises. The company handled maintenance and cybersecurity for a core Army backbone network.}
        \item {Created lesson plans and materials on network fundamentals for the company induction programme. This addressed the problem of lost knowledge and expertise in a company with high turnover rate.}
      \end{cvitems}
    }
  \cventry
    {IT Analyst, Intern}
    {GIC Pte Ltd, Technology Department}
    {Singapore}
    {Sep. 2014 – Feb. 2015}
    {
      \begin{cvitems}
        \item {Designed and developed a version control program and process in shell for source code deployment and code version integrity of clients and servers of the investment management system deployed worldwide.}
        \item {Proposed and prototyped Splunk dashboards for real-time analysis and alert notifications on server health.}
      \end{cvitems} 
    }
\end{cventries}
