\cvsection{Extracurricular Activity}
\begin{cventries}
  \cventry
    {Peer Mentor}
    {Monash University Faculty of IT Peer Mentor Programme}
    {Victoria, Australia}
    {Jun. 2018 - PRESENT}
    {
      \begin{cvitems}
        \item {Led orientation activities, helped with monthly events for first-year IT students, and provided general support for academic help and adjustment to university life.}
      \end{cvitems}
    }
    \cventry
    {Sub-Committee, Events and Logistics}
    {Singapore Association of Monash}
    {Victoria, Australia}
    {Oct. 2017 - PRESENT}
    {
      \begin{cvitems}
        \item {Initiated a mentorship programme for first-year students from Singapore to soften the transition of moving to a new environment for studies. Assisted with the running of various on-campus club events.}
      \end{cvitems}
    }
   \cventry
    {President}
    {Temasek Polytechnic Stargazers (Astronomy Club)}
    {Singapore}
    {2014 - 2015}
    {
      \begin{cvitems}
        \item {Worked with a lecturer to propose the establishment of the club and secured \$10,000 worth of funding for the first astronomy club at Temasek Polytechnic. Formed a team to organise events and built working relationships with other astronomy clubs in Singapore.}
      \end{cvitems}
    }
    \cventry
    {Honorary Secretary and Project Leader}
    {Temasek Polytechnic Enactus (Social Entrepreneurship Club)}
    {Singapore}
    {2013 - 2015}
    {
      \begin{cvitems}
        \item {Prepared discussion items and minutes for executive committee meetings.}
        \item {Worked with SAMH (Singapore Association for Mental Health) to sell art and handicraft made by residents recovering from mental health illnesses.}
      \end{cvitems}
    }
\end{cventries}
